% !TEX program = xelatex
\documentclass[letterpaper,10pt]{article}
\usepackage{styles/resume-professional}

% Function inputs for info
\input{info/batuhan.tex}

\begin{document}

%----------HEADING----------
\begin{center}
  {\Large \myname, \mytitle}
  \\
  \vspace{0pt}
  \faMobile \enspace
  {\myphone} ~
  \textbullet
  \faEnvelope \enspace
  \href{mailto:\myemail}{\color{blue}{\myemail}} ~
  \textbullet
  \faHome \enspace
  {\mylocation} ~
  \textbullet
  \faMap \enspace
  {Green Card Holder}
  \\
  \faLinkedin \enspace
  \href{https://www.linkedin.com/in/\mylinkedin}{\color{blue}{\mylinkedin}} ~
  \textbullet
  \faGithub \enspace
  \href{https://github.com/\mygithub}{\color{blue}{\mygithub}} ~
  \textbullet
  \faTwitter \enspace
  \href{https://twitter.com/bbaserdem}{ \color{blue}{bbaserdem}}
  \vspace{-9pt}
\end{center}

%-----------INTRO-------------
\begin{center}
  Research scientist in Neuroscience with Physics background,
  experienced with using Reinforcement Learning and Machine Learning
  to model the brain and animal behavior.
  Interested in conducting research and developing ML systems for
  complex problems.

\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart
% Skyfi
\resumeSubheading
{Software Engineer}
{Austin, TX, USA}
{SkyFi}
{2025}
\resumeItemListStart
\resumeItem{\textbf{Developed analytical toolkits for image detection}
  to use in geospatial imaging analytical toolkit, using low level
interaction with modern AI toolkits.}
\resumeItem{\textbf{Created maintainable codebase} for analytical analysis,
ensuring usability of the codebase for collaborations across disciplines.}
\resumeItemListEnd

% CSHL Graduate
\resumeSubheading
{Graduate Researcher}
{Cold Spring Harbor, NY, USA}
{Cold Spring Harbor Laboratory, Koulakov Laboratory}
{2016 - 2023}
\resumeItemListStart
\resumeItem{\textbf{Developed and trained reinforcement learning
  models} interfacing with fluid dynamics to simulate odor navigation
  tasks in-silico; successfully reproduced known animal behavior in a
non-supervised setting.}
\resumeItem{\textbf{Built machine learning and statistical analysis
  pipelines} in collaboration with multiple laboratories, leading to
  the discovery of previously unknown structural patterns in the mouse
brain through large-scale data analysis.~\cite{mapseq}}
\resumeItem{\textbf{Designed and scaled simulations of genetic
  network self-assembly}, achieving a 20$\times$ runtime optimization
  to enable larger simulations, which validated key hypotheses in
neural tissue modeling.~\cite{connclone}}
\resumeItemListEnd

% CSHL Postdoc
\resumeSubheading
{Post-Doctorate Researcher}
{Cold Spring Harbor, NY, USA}
{Cold Spring Harbor Laboratory, Koulakov Laboratory}
{2023 -2024}
\resumeItemListStart
\resumeItem{\textbf{Developed advanced Python pipelines} to process
  and align large-scale imaging datasets, streamlining data workflows
across multiple laboratories and improving analysis efficiency.}
\resumeItem{\textbf{Applied machine learning algorithms for image
  processing} and data denoising, enhancing data quality and
consistency for complex imaging projects.}
\resumeItemListEnd

% AI Resident
\resumeSubheading
{AI Fellowship}
{Lowell, VT, USA}
{Monastic Academy For the Preservation of Life on Earth (MAPLE)}
{2024 - 2025}
\resumeItemListStart
\resumeItem{\textbf{Participated in AI safety studies} on aligning AI
with Buddhism.}
\resumeItemListEnd

% OHSU intern
% \resumeSubheading
% {Research Intern}
% {Portland, OR, USA}
% {Oregon Health \& Science University}
% {January 2013}
% \resumeItemListStart
% \resumeItem{Supported intraoperative neuro-monitoring during spinal
%   surgeries, conducting analysis on patient data to assess the
% effectiveness of neuro-monitoring techniques in reducing nerve damage risks.}
% \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8pt}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
% Stony Brook
\resumeSubheading
{Stony Brook University}
{Stony Brook, NY, USA}
{Ph.D. Physics}
{August 2014 - August 2023}
\resumeItemListStart
\resumeItem{
  Dissertation title:
  Studying Neural Computation Through Connectomics
}
\resumeItem{
  Studied reinforcement learning, machine learning, statistical
  analysis, and optimization under Prof. Alexei Koulakov.
}
\resumeItem{
  Worked as a Teaching Assistant for both graduate and undergraduate courses.
}
\resumeItemListEnd

% AI Resident
\resumeSubheading
{Gauntlet AI}
{Austin, TX, USA}
{AI Challenger}
{2025}
\resumeItemListStart
\resumeItem{\textbf{Participated in AI assisted coding challenge} on
AI coding incubator.}
\resumeItem{\textbf{Developed 9 applications in 10 weeks}, leveraging
AI for coding and research into new coding disciplines.}
\resumeItem{\textbf{Collaborated in developing new workflows} with
  people of different backgrounds; accelerating AI assisted development
processes.}
\resumeItemListEnd

\resumeSubheading
{Boğaziçi University}
{Istanbul, Turkey}
{B.Sc. Physics}
{2010 - 2014}
\resumeItemListStart
\resumeItem{
  Relevant courses:
  Group Theory, Statistical Mechanics, C Programming, Information Theory
}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8pt}
%-----------SKILLS-----------
\section{SKILLS}

\begin{multicols}{2}
  \begin{tabular}{ p{5.4cm} p{14.3cm}}
    \textbf{Programming languages}    & Python, C, C++, R, MATLAB, Rust \\
    \textbf{Machine Learning}         & Reinforcement Learning,
    Unsupervised Learning, Transformer Neural Networks \\
    \textbf{Tools and Platforms}         & PyTorch, Unix, Linux, Nix, Git,
    Docker, AWS, OpenFOAM, Generative AI \\
    \textbf{Data Analysis \& Modelling}         & Statistical
    Analysis, Linear Algebra, Differential Geometry, Fluid Mechanics \\
    \textbf{Interests}         & Knowledge Graphs, Graph
    Transformers, Anomaly Detection \\
  \end{tabular}
\end{multicols}

%-----------Publications---------------
%
\printbibliography[title = PUBLICATIONS]
\vspace{-10pt}

\end{document}
