% !TEX program = xelatex
\documentclass[letterpaper,11pt]{article}
\usepackage{styles/resume-professional}

% Function inputs for info
\input{info/batuhan.tex}

\begin{document}
% To force all papers to show up
\nocite{*}

%----------HEADING----------
\begin{center}
    {\huge \myname, \mytitle}
    \\
    \vspace{2pt} 
    \faMobile \enspace
    {\myphone} ~ 
    \textbullet
    \faEnvelope \enspace
    \href{mailto:\myemail}{\color{blue}{\myemail}} ~ 
    \textbullet
    \faHome \enspace
    {\mylocation} ~ 
    \textbullet
    \faMap \enspace
    {Green Card Holder}
    \\
    \faLinkedin \enspace
    \href{https://www.linkedin.com/in/\mylinkedin}{\color{blue}{\mylinkedin}} ~
    \textbullet
    \faGithub \enspace
    \href{https://github.com/\mygithub}{\color{blue}{\mygithub}} ~
    \textbullet
    \faTwitter \enspace
    \href{https://twitter.com/bbaserdem}{ \color{blue}{bbaserdem}}
    \vspace{-7pt}
\end{center}

%-----------INTRO-------------
\begin{center}
Research scientist in Neuroscience with Physics background,
experienced with using Reinforcement Learning and Machine Learning to model the brain and animal behavior.
Interested in conducting research and developing ML systems for complex problems.

\end{center}
 
%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    % Stony Brook 
    \resumeSubheading
      {Stony Brook University}
      {Stony Brook, NY, USA}
      {Ph.D. Physics}
      {August 2014 - August 2023}
      \resumeItemListStart
        \resumeItem{
          Dissertation title:
          Studying Neural Computation Through Connectomics
        }
        \resumeItem{
          Studied reinforcement learning, machine learning, statistical analysis, and optimization under Prof. Alexei Koulakov.
        }
        \resumeItem{
          Worked as a Teaching Assistant for both graduate and undergraduate courses.
        }
      \resumeItemListEnd

    \vspace{-4pt}

    \resumeSubheading
      {Boğaziçi University}
      {Istanbul, Turkey}
      {B.Sc. Physics}
      {2010 - 2014}
      \resumeItemListStart
        \resumeItem{
          Relevant courses:
          Group Theory, Statistical Mechanics, C Programming, Information Theory
        }
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{-10pt}

 %-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    % CSHL Graduate
    \resumeSubheading
      {Graduate Researcher}
      {Cold Spring Harbor, NY, USA} 
      {Cold Spring Harbor Laboratory, Koulakov Laboratory}
      {August 2016 - August 2023}
      \resumeItemListStart
        \resumeItem{Developed and trained reinforcement learning models interfacing with fluid dynamics to simulate odor navigation tasks in-silico; successfully reproduced known animal behavior in a non-supervised setting.}
        \resumeItem{Used machine learning and developed statistical analysis pipeline in a multi-laboratory collaboration, which lead to the discovery of previously unknown structure in the mouse brain.~\cite{mapseq}}
        \resumeItem{Designed simulations of self-assembly of genetic networks, demonstrating a possible method for cloning neural tissue.~\cite{connclone} Optimized the runtime of the simulations by 20-fold, allowing the work to be extended to larger networks and solidifying our findings.}
      \resumeItemListEnd
    % CSHL Postdoc
    \resumeSubheading
      {Post-Doctorate Researcher}
      {Cold Spring Harbor, NY, USA} 
      {Cold Spring Harbor Laboratory, Koulakov Laboratory}
      {August 2023 - September 2024}
      \resumeItemListStart
        \resumeItem{Developed Python-based pipelines to analyze and align large-scale imaging datasets, improving data efficiency across multiple labs. Applied machine learning techniques for image processing and data denoising.}
      \resumeItemListEnd
    % OHSU intern
    \resumeSubheading
      {Research Intern}
      {Portland, OR, NY} 
      {Oregon Health \& Science University} 
      {January 2013}
      \resumeItemListStart
            \resumeItem{Assisted neuro-monitoring during spinal surgeries under Dr. Ilker Yaylali M.D., Ph.D.}
            \resumeItem{Analysed historic patient data to evaluate the efficacy of neuro-monitoring during spinal surgeries in preventing permanent nerve damage.}
      \resumeItemListEnd  

  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------SKILLS-----------
\section{SKILLS}

  \begin{multicols}{2}
    \begin{tabular}{ p{5.4cm} p{14.3cm}}
      \textbf{Programming languages}    & Python, C, C++, R, MATLAB \\
      \textbf{Machine Learning}         & Reinforcement Learning, Unsupervised Learning, Transformer Neural Networks \\
      \textbf{Tools and Platforms}         & PyTorch, Unix, Linux, Git, AWS, OpenFOAM \\
      \textbf{Data Analysis \& Modelling}         & Statistical Analysis, Linear Algebra, Differential Geometry, Fluid Mechanics \\
    \end{tabular}
  \end{multicols}

%-----------Publications---------------
%
\printbibliography[title = PUBLICATIONS]
\vspace{-8pt}

\end{document}

