% !TEX program = xelatex

% All preamble is in resumeProfessionalTemplate-vaishanth.sty
\documentclass[letterpaper,11pt]{article}
\usepackage{styles/resume-professional}

% Function inputs for info
\input{info/batuhan.tex}

\begin{document}
\nocite{*}

%----------HEADING----------
\begin{center}
    {\huge \myname, \mytitle}
    \\
    \vspace{2pt} 
    \faMobile \enspace
    { \myphone } ~ 
    \textbullet
    \faEnvelope \enspace
    \href{mailto:[\myemail]}{\color{blue}{\myemail}} ~ 
    \textbullet
    \faHome \enspace
    {\mylocation} ~ 
    \textbullet
    \faMap \enspace
    {Green Card Holder}
    \\
    \faLinkedin \enspace
    \href{[https://www.linkedin.com/in/\mylinkedin]}{\color{blue}{\mylinkedin}} ~
    \textbullet
    \faGithub \enspace
    \href{[https://github.com/\mygithub]}{\color{blue}{\mygithub}} ~
    \textbullet
    \faTwitter \enspace
    \href{[https://twitter.com/bbaserdem]}{ \color{blue}{bbaserdem}}
    \vspace{-7pt}
\end{center}
 
%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    % Stony Brook 
    \resumeSubheading
      {Stony Brook University}
      {Stony Brook, NY, USA}
      {Ph.D. Physics}
      {August 2014 - August 2023}
      \resumeItemListStart
        \resumeItem{
          Dissertation title:
          Studying Neural Computation Through Connectomics
        }
        \resumeItem{
          Relevant courses:
          Group Theory, Statistical Mechanics, Quantum Field Theory, General Relativity
        }
        \resumeItem{
          Worked as a Teaching Assistant for both graduate and undergraduate courses.
        }
      \resumeItemListEnd

    \vspace{-4pt}

    \resumeSubheading
      {Boğaziçi University}
      {Istanbul, Turkey}
      {Bsc Physics}
      {2010 - 2014}
      \resumeItemListStart
        \resumeItem{
          Relevant courses:
          Group Theory, Statistical Mechanics, C Programming, Information Theory
        }
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{-10pt}

 %-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Post-Doctorate Researcher}
      {Cold Spring Harbor, NY, USA} 
      {Cold Spring Harbor Laboratory, Koulakov Laboratory}
      {August 2023 - September 2024}
      \resumeItemListStart
        \resumeItem{Organized, reformatted and documented large imaging datasets collected by different laboratories to have a unified interface through MATLAB.}
        \resumeItem{Designed and implemented data analysis pipeline that denoises and aligns large imaging datasets in Python.}
        % LEFT IT HERE
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Researcher}
      {Cold Spring Harbor, NY, USA} 
      {Cold Spring Harbor Laboratory, Koulakov Laboratory}
      {August 2016 - August 2023}
      \resumeItemListStart
        \resumeItem{Conducted research with PhD advisor Prof. Alexei Koulakov}
        \resumeItem{Participated in peer discussions, and presentations to wider academic audience.}
        \resumeItem{Leveraged reinforcement learning (RL), machine learning (ML), statistical analysis, and optimization.}
        \resumeItem{Designed and programmed simulations for self-assembly of genetic networks, and published our findings.~\cite{connclone}}
        \resumeItem{Collaborated on a multi-laboratory project, and produced statistical analysis methods which lead to the discovery of structure in the mouse brain.~\cite{mapseq}}
        \resumeItem{Designed a model environment that simulates animal behavioral learning using fluid mechanics and reinforcement learning.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern}
      {Portland, OR, NY} 
      {Oregon Health \& Science University} 
      {January 2013}
      \resumeItemListStart
            \resumeItem{Assisted neuro-monitoring during spinal surgeries under Dr. Ilker Yaylali M.D., Ph.D.}
            \resumeItem{Analysed historic patient data to evaluate the efficacy of neuro-monitoring during spinal surgeries in preventing permanent nerve damage.}
      \resumeItemListEnd  

    % copy and paste above resumeSubheading block to add more 
  \resumeSubHeadingListEnd
\vspace{-12pt}
%-----------SKILLS-----------
\section{SKILLS}
  \begin{itemize}[leftmargin=0in, label={}] \small{ \item{
    \textbf{\normalsize{Programming:}}{\normalsize{
      Python, C, C++, R, MATLAB, PyTorch, Unix, Linux, Git, AWS, OpenFOAM
    }} \\ \vspace{1.2pt}  
    \textbf{\normalsize{Machine Learning:}}{\normalsize{
      Reinforcement Learning, Unsupervised Learning, Transformer Neural Networks
    }} \\ \vspace{1.2pt}
      
    \textbf{\normalsize{Academic:}}{\normalsize{
      Linear Algebra, Differential Geometry, Statistical Mechanics, Smoothed Particle Hydrodynamics, Quantum Field Theory
    }}

     % copy and paste above textbf block to add more 
  } }\end{itemize}
 \vspace{-16pt}

%-----------Publications---------------
%
\printbibliography[title = PUBLICATIONS]
      
\vspace{-8pt}

\end{document}

